### 2021-04-01 papers.tex
fix badge overlapping text

\addtrack{}{(Meta)physics}
\addpaper
    {A Complete Survey of 0-Dimensional Computer Graphics}
    {Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Po Po}
    {Keywords: Computer Graphics, Geometry, Rendering, Animation}
    {SIGBOVIK_2021_paper_30}
    {0cm}
    {}
\addpaper
    {Macro-driven metalanguage for writing Pyramid Scheme programs}
    {Marcin Konowalczyk}
    {Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
    {SIGBOVIK_2021_paper_31}
    {0cm}
    {\badges{\hspace{0.5in}\badge{mlm}}}
\addpaper
    {On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
    {Zikuan Wang}
    {Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
    {SIGBOVIK_2021_paper_32}
    {0cm}
    {}
\addpaper
    {Inverted Code Theory: Manipulating Program Entropy}
    {usH nalA dna eiX xelA}
    {Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}
    {SIGBOVIK_2021_paper_23}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}

>>>>

\addtrack{}{(Meta)physics}
\addpaper
    {A Complete Survey of 0-Dimensional Computer Graphics}
    {Hesper Yin, Oscar Dadfar, Max Slater, Anne He, Alice Lai, Emma Liu and Po Po}
    {Keywords: Computer Graphics, Geometry, Rendering, Animation}
    {SIGBOVIK_2021_paper_30}
    {0cm}
    {}
\fancypagestyle{fancypyramid}{\fancyheadoffset[roh]{0.75in}}
\addpaper
    [fancypyramid]
    {Macro-driven metalanguage for writing Pyramid Scheme programs}
    {Marcin Konowalczyk}
    {Keywords: syntax tree, pyramids, compilation, horizontal gene transfer, sorting, code golf}
    {SIGBOVIK_2021_paper_31}
    {0cm}
    {\badges{\badge{mlm}}}
\addpaper
    {On the fundamental impossibility of refining the Theory of Everything by empirical observations: a computational theoretic perspective}
    {Zikuan Wang}
    {Keywords: Theory of Everything, Cellular Automaton, Emulation, the Universe}
    {SIGBOVIK_2021_paper_32}
    {0cm}
    {}
\addpaper
    {Inverted Code Theory: Manipulating Program Entropy}
    {usH nalA dna eiX xelA}
    {Keywords: Tenet, Inverted, Temporal Pincer, Entropy, Turnstile, Inverted Code Theory, P vs. NP, Quantum Computing, Reinforcement Learning}
    {SIGBOVIK_2021_paper_23}
    {0cm}
    {}
\addreview
    {SIGBOVIK_2021_review_2}
    {0cm}
